### 2015-03-02 fundamentals/conclusion.tex
less redundancy, as suggested by @flanflanagan
more clarity, as suggested by @flanflanagan

The \Cyclus nuclear fuel cycle framework presents a more generic and flexible
alternative to existing fuel cycle simulators. Where previous nuclear fuel cycle simulators have had limited distribution,
constrained simulation capabilities, and restricted customizability, \Cyclus emphasizes an
open strategy for access and development.  This open strategy, with transparent
publication of the source code, not only provides much-needed accessibility,
but also enables transparency and community oversight.

@@

Similarly, discrete, fidelity-agnostic object tracking facilitates simulations
at every level of detail. Simulations relying on arbitrarily complex isotopic
compositions are possible in \Cyclus, as are simulations not employing any
physics at all. Indeed, agents of such varying fidelity can even exist in the
same simulation. Researchers no longer need to reinvent the wheel in order to
model a simulation focused on the aspects of the fuel cycle
relevant to their research.

>>>>

The \Cyclus nuclear fuel cycle framework presents a more generic and flexible
alternative to existing fuel cycle simulators. Where previous nuclear fuel
cycle simulators have had limited distribution, constrained simulation
capabilities, and restricted customizability, \Cyclus emphasizes an open
strategy for access and development.  This open strategy not only improves
accessibility, but also enables transparency and community oversight.

@@

Similarly the fidelity-agnostic modular architecture facilitates simulations
at every level of detail. Simulations relying on arbitrarily complex isotopic
compositions are possible in \Cyclus, as are simulations not employing any
physics at all. Indeed, agents of such varying fidelity can even exist in the
same simulation. Researchers no longer need to reinvent the wheel in order to
model a simulation focused on the aspects of the fuel cycle
relevant to their research.
